## Cobind Reproduction Summary

```{r setup,echo=FALSE,eval=FALSE}

.libPaths(c("~/rlibs/4.0.4/",.libPaths()))

```

### General Idea

In the cobind paper, XXXAUTHORSXXX, the authors measure collocation between bedfiles delineating binding sites output by REMAP2 and a single bedfile taken from ENCODE containing the binding sites for CTCF. The idea is to demonstrate that the CBF regions from REMAP2 with the most "similarity" with the bedfile from ENCODE would be those with the greatest shared biological function.

### Data


```{bash data, eval=FALSE, echo=TRUE}
outdir=~/interval_sketch/hammock/cobind_repro/data
datadir=/data/blangme2/jessica/remap2022
mkdir $datadir
results=~/interval_sketch/hammock/cobind_repro
cd $datadir
mkdir subbeds
wget https://remap.univ-amu.fr/storage/remap2022/hg38/MACS2/remap2022_crm_macs2_hg38_v1_0.bed.gz
gunzip remap2022_crm_macs2_hg38_v1_0.bed.gz 
bedfile1="remap2022_crm_macs2_hg38_v1_0.bed"
# get the fourth column from the bedfile and remove duplicates
proteins1=$(sed 's/\t/|/g' $bedfile1 | cut -d'|' -f4 | sort -u)
# Split lines around any other delimiters; dedup; get rid of commas at ends of lines.
proteins=$(echo $proteins1 | tr ',' '\n' | tr ' ' '\n'| sort -u | tr '\n' ',' | sed 's/,$//')
# write out with each protein/gene name on a new line 
echo $proteins | tr ',' '\n' > proteins.txt

# Split the bedfile into 2 sub-bedfiles for each unique protein name: all columns,only first 3 columns
for name in $(echo $proteins| tr ',' ' '); do
  grep $name $bedfile1 > subbeds/${name}_hg38.bed
  awk -v name=$name -v OFS="\t" '{print $1,$2,$3}' subbeds/${name}_hg38.bed > subbeds/${name}_hg38_c3.bed
done

# make files holding global paths to each of the sub-bed files ... also remove any empty ones jic
find subbeds -type f -empty -delete

find $PWD/subbeds/*hg38.bed -maxdepth 1 -type f > TFbeds.txt
find $PWD/subbeds/*hg38_c3.bed -maxdepth 1 -type f > TFbeds_c3.txt

cd $outdir
ln -s ${datadir}/* .

# obtain ENCODE bedfile for comparison
wget https://www.encodeproject.org/files/ENCFF660GHM/@@download/ENCFF660GHM.bed.gz
gunzip ENCFF660GHM.bed.gz 

# create primary comparison file path list (the "ones" in 1-to-many comparison)
find $outdir/ENCFF660GHM.bed -type f > TFbeds_primary.txt
grep CTCF_ ${datadir}/TFbeds_c3.txt >> TFbeds_primary.txt

```

```{bash jaccards, echo=TRUE, eval=FALSE, cache=TRUE}
datadir=~/interval_sketch/hammock/cobind_repro/data
resultsdir=~/interval_sketch/hammock/cobind_repro/results_preham
codedir=~/interval_sketch/hammock/lib
cd $resultsdir
#python3 ${codedir}/bed_jaccards_parallel_1m.py ${datadir}/TFbeds.txt ${datadir}/TFbeds_primary.txt C remap_encode

grep CTCF_ remap_encode_jaccC.csv | sort -k4 -t, -n -r | grep -n -f ${datadir}/TFs_CTCF.txt 
grep ENCFF660GHM remap_encode_jaccC.csv | sort -k4 -t, -n -r | grep -n -f ${datadir}/TFs_CTCF.txt 
grep ENCFF660GHM remap_encode_jaccC.csv | sort -k4 -t, -n -r | grep -n ,CTCF_
```

```{bash cobind,echo=TRUE, cache=TRUE}
datadir=~/interval_sketch/hammock/cobind_repro/data
resultsdir=~/interval_sketch/hammock/cobind_repro/results_preham
cd $resultsdir
#pip install git+https://github.com/liguowang/cobind.git
item=0
rm cobind_CTCF1.txt
for tfbed in $(grep -f ${datadir}/TFs_CTCF.txt ${datadir}/TFbeds.txt) ; do 
  cobind.py jaccard ${datadir}/ENCFF660GHM.bed ${tfbed} | awk -v val=$item '{print(val,$0)}' >> cobind_CTCF1.txt
  item=$(($item + 1))
  cobind.py jaccard ${datadir}/subbeds/CTCF_hg38_c3.bed ${tfbed}| awk -v val=$item '{print(val,$0)}' >> cobind_CTCF1.txt
  item=$(($item + 1))
done
cobind.py jaccard ${datadir}/ENCFF660GHM.bed ${datadir}/subbeds/CTCF_hg38_c3.bed | awk -v val=$item '{print(val,$0)}' > cobind_CTCF2.txt
cat cobind_CTCF?.txt | sed 's/\% /\%/g' > cobind_CTCF.txt

item=0
for tfbed in $(cat ${datadir}/TFbeds.txt) ; do 
  cobind.py jaccard ${datadir}/ENCFF660GHM.bed ${tfbed} | awk -v val=$item '{print(val,$0)}' >> cobind_ALL1.txt
  item=$(($item + 1))
  cobind.py jaccard ${datadir}/subbeds/CTCF_hg38_c3.bed ${tfbed}| awk -v val=$item '{print(val,$0)}' >> cobind_ALL1.txt
  item=$(($item + 1))
done
cobind.py jaccard ${datadir}/ENCFF660GHM.bed ${datadir}/subbeds/CTCF_hg38_c3.bed | awk -v val=$item '{print(val,$0)}' > cobind_ALL2.txt
cat cobind_ALL?.txt | sed 's/\% /\%/g' > cobind_ALL.txt


#cat cobind_CTCF.txt | sed -i 's/\% /\%/g' cobind_CTCF.txt 

```

### Sketch Commands
```{bash sketch}


datadir=~/interval_sketch/hammock/cobind_repro/data
resultsdir=~/interval_sketch/hammock/cobind_repro/results_preham
codedir=~/interval_sketch/hammock/lib
cd $resultsdir

python3 ${codedir}/bed_jaccmh_parallel_1m.py ../data/TFbeds.txt ../data/TFbeds_primary.txt C 10000 remap_encode 

grep ^CTCF_ ctcf_brca_m1_mh_p10000_jaccA.csv | sort -k3 -t, -n -r | grep -n -f ../data/TFs_CTCF.txt 


```



### Results


```{r dataprep}
cobindo <- fread("./results_preham/cobind_CTCF.txt",fill=TRUE,sep=" ") %>%
  rename(id=V1, name=V2, value=V3) %>% 
  pivot_wider(id_cols = id, names_from = name,values_from = value ) #%>% select(A.name,B.name,starts_with("Coef"))
cobindo$B.name <- gsub(".bed", "", gsub("_hg38","", x=gsub("_c3","",x=cobindo$B.name)))
cobindo$A.name <- gsub(".bed", "", gsub("_hg38","", x=gsub("_c3","",x=cobindo$A.name)))

sketch <- fread("./results_preham/10000_p10000_jaccA.csv") %>% rename(A.name=bed1, B.name=bed2, sketchA=jaccA)
sketch$B.name <- gsub(".bed", "", gsub("_hg38","", x=gsub("_c3","",x=sketch$B.name)))
sketch$A.name <- gsub(".bed", "", gsub("_hg38","", x=gsub("_c3","",x=sketch$A.name)))

tfs <- fread("./results_preham/remap_encode_jaccC.csv") %>% rename(A.name=bed1, B.name=bed2)
tfs$B.name <- gsub(".bed", "", gsub("_hg38","", x=gsub("_c3","",x=tfs$B.name)))
tfs$A.name <- gsub(".bed", "", gsub("_hg38","", x=gsub("_c3","",x=tfs$A.name)))

papero <- fread("./data/SupplementaryTables_S1.csv",skip =1) %>% rename(B.name=TF_name) %>%
  select(B.name,J)

comparison <- full_join(cobindo %>% select(A.name,B.name,starts_with("Coef")),tfs) %>% full_join(papero)

```

